---
title: "Create CSV file of Future Workshops"
subtitle: "Data are from the LibCal API, parsed by rvest and dplyr"
date: "`r Sys.Date()`"
output: html_notebook
---

1. Run this at the beginning of the semester to generate the main workshop list
1. Use this to generate the workshop flyer, for advertising
1. This script depends on `01_gather_and_wrangle.R` to harvest the data

## Release Notes

- August 10, 2021:  Undertook this revision because the integration of online and in-person workshops made Joel's script ineffective.  Nonetheless, borrowed heavily from his previous work.  The RMD migration of Joel's `rvestLibcalCode.R`

## library packages

```{r message=FALSE, warning=FALSE}
Sys.setenv(TZ="America/New_York")
library(fs)
```

## Get Data

Ingest data from web page (LibCal API) & make a column headers template for the attendance sheets that will be written to Google.

### harvest webpage data from LibCal API

this next CODE CHUNK is DISABLED, but designed to rerun the harvest script


```{r get wrangled data, include=FALSE}
source("01_gather_and_wrangle.R", local = knitr::knit_global())
# or sys.source("your-script.R", envir = knitr::knit_global())
```

## Wrangle Data

```{r}
for_goog_flyer_df <- my_df %>% 
    select_if(is.character) %>% 
    select(workshop_id, date, day = day_flyer, title, presenter,  online_in_person = online_in_person_flyer,
           time = time_flyer, workshop_begins = begins_display, workshop_ends = ends_display, 
           workshop_duration_minutes, description, registration_link, location) 
```



## Write output

Manually move, and rename, the google sheet into the proper CDVS google drive space.

```{r}
fs::dir_create("output")

fs::file_copy("output/workshops.csv", 
              glue::glue("output/workshops.bak.{Sys.Date()}.{round(Sys.getpid() * runif(1))}.csv"))

write_csv(my_df, "output/workshops.csv")

write_csv(for_goog_flyer_df, "output/forgoog_flyer.csv")  
```

## For Flyer -- Upload manully to Google Sheets.  

```{r eval=FALSE, include=FALSE}
# googlesheets4::gs4_create("Main Workshop list for Semester", sheets = list(sname = my_df))

googlesheets4::gs4_create("Main Workshop list for Semester",
                          sheets = list(Sheet1 = for_goog_flyer_df),
                          timeZone = "America/New_York")
```

### above chunk may have to be be run manually.  It will upload to your google drive home directory (Check "recent" on google drive).  Then move to the proper spot.  **BE SURE TO CHECK THE DATES**.  Google drive has a tendency to fock up the dates and impose GMT instead of EST!!   I noticed this when mnaully uploading.  See next...

### Manually upload `for_googflyer.csv` to:  `Google Drive > CDVS > Services > Workshops > [2021 Fall] > Planning`

By spring of 2022 this problem had resolved but in the fall of 2021 there were extraneous leading single apostrophes showing up in the uploaded data.  This was probably a bug with `library(googlesheets4)`. The manual work-around, instead of `gs4_create()`, was to upload the forgoog_flyer.csv file **manually** to Google Drive, then open the csv on Google Drive, and then "Open With" as a Sheet.  BUT, this allowed Google to force it's own GMT timezone.  So, you have to opea blank sheet (sheets.new), Then `import`, then be sure not to allow any automatic conversion of fields (this is an option in the later stages of the import.)
