---
title: "Create Attendance Worksheets"
output: html_notebook
---

Make one blank attendance template for each workshop. Write each blank template to Google Drive as a spreadsheet. 

## Library Packages

```{r message=FALSE, warning=FALSE, include=FALSE}
Sys.setenv(TZ="America/New_York")
library(rvest)
library(clock)
library(tidyverse)
library(fs)
library(googlesheets4)
```

## Get Data

Ingest data from web page (LibCal API) & make a column headers template for the attendance sheets that will be written to Google.

### harvest webpage data from LibCal API

this next CODE CHUNK is DISABLED, but designed to rerun the harvest script.  INSTEAD skip to the `ingest_csv` code chunk.

```
{r get wrangled data, include=FALSE}
source("01_gather_and_wrangle.R", local = knitr::knit_global())
# or sys.source("your-script.R", envir = knitr::knit_global())
```

Since the API can only be used at the beginning of the semester, and since `01_gather_and_wrangle.R` was already called (by `02_foo.Rmd`) and generated `output/workshops.csv`, here, rather, we will simply ingest the file output/workshops.csv.  NOTE: `01_gather_and_wrangle.R`, if run after the beginning fo the semester, will overwrite `workshops.csv`.  In this case, use `read_csv()` to import one of the back-up files found in the `output` directory.

```{r ingest csv, message=FALSE, warning=FALSE, include=FALSE}
my_df <- read_csv("output/workshops.csv")
```


### worksheets template header

make a vector of column headings that will become the headings of the google sheests attendance records

```{r}
blank_df <- tibble("Attended (x or blank)" = NA,
                "Registration Status (Registered, Waitlist, or Walk-in)"  = NA,
                "First Name" = NA,
                "Last Name" = NA,
                "Email" = NA,
                "Booking Made" = NA,
                "Attendance" = NA,
                "Are you affiliated with Duke University, Duke Medical Center, DCRI, or another Duke group?" = NA,
                "Academic Status (or other)" = NA,
                "Discipline or Affiliation" = NA,
                "Institutes, Initiatives, or Program Affiliation" = NA,
                "Where did you hear about this event?" = NA,
                "Have you consulted with Data and Visualization Services before this workshop?" = NA,
                "Would you like to receive more information about DVS events and training?" = NA,
                "I'm interested in registering for this workshop because:" = NA,
                "If other, describe below:" = NA)
```

## Wrangle

```{r}
my_df <- my_df %>% 
    bind_cols(blank_df) %>% 
    rename(`Workshop Date` = date) %>%
    select(`Attended (x or blank)`, 
           `Registration Status (Registered, Waitlist, or Walk-in)`,
           `Workshop Date`,
           `Workshop Name` = title,
           `WorkshopID` = workshop_id,
           `First Name`:last_col())
```


## Upload to Google Drive

The following code chunks are manually disabled because they write files to google drive.  This is "belt and suspenders" caution.  To enable the code-blocks, remove the carriage-return at the end of the third backtick and before the first open curly brace.

After uploaded to Google Account's homedrive, ...  
Move to  `Google Drive > CDVS > Services > Workshops > [2021 Fall] > Attendance`

```
{r}
workshop_list_to_upload_into_GoogleDrive <- my_df %>% 
   rowwise() %>%
   group_map(tibble)  # make each row it's own tibble

walk(
  workshop_list_to_upload_into_GoogleDrive,
  ~ gs4_create(.$`Workshop Name`, sheets = list(attendance = .))
)
```

