---
title: "Duke Events Calendar"
output: html_notebook
---

This is a report Sophia uses to send to the Duke Events people.  This gets our workshops up on the **Big Board**

```{r}
library(tidyverse)
library(here)
library(fs)
library(glue)
```


```{r}
my_df <- read_csv("output/workshops.csv")
DVS_workshop_schedule <- my_df 
```

```{r}
glimpse(my_df)
```

## Duke Events Report

Create The Duke Events Report.  From the previous version, the following fields are needed.

- Title
- Presenter
- Series Name
- Co-sponsors
- Date  (Must be miliarty time.)
- Start Time Clean
- End Time Clean
- Duration in hours
- Plain Text Descriptions
- Location


```{r}
duke_events <- DVS_workshop_schedule %>% 
  mutate(series_title = "Center for Data and Visualization Sciences (CDVS) Workshop Series",
         co_sponsors = "SSRI, Research Computing",
         duration_in_hours = (workshop_duration_minutes / 60),
         title = paste0("CDVS Workshop: ", title),
         contact = "Joel Herndon"
         ) %>% 
  mutate(start_time = format(workshop_begins, "%H:%M")) %>% 
  mutate(end_time = format(workshop_ends, "%H:%M")) %>% 
  select(title, presenter, series_title, 
         co_sponsors, 
         date, start_time, 
         end_time, duration_in_hours, 
         description,
         registration_link, 
         location, contact
         ) %>% 
  mutate(date = format(date, "%Y-%m-%d")) 


duke_events
```



### Write Duke Events CSV file

1. Creates "output" directory if it doesn not already exist (or leave's it alone if it does)
1. Write's a duke_events.csv report file in the "output" directory

```{r}
dir_create("output")
write_csv(duke_events, 
          here("output", glue(
            glue(
              "duke_events_from_dvs_workshops",
              format(Sys.Date(), "%Y-%m-%d"),
              .sep = "_"
            ),
            "csv",
            .sep = "."
          )))
```